The Inconsistency in G\"odel's Ontological Argument: \\ A Success Story for AI in Metaphysics

### 2016-01-29 Papers/InProgress/IJCAI/submission.tex
further improvements

@@

@@

\begin{figure}
\centerline{\includegraphics[width=.95\columnwidth]{./Images/UglyEssence.png}}
\caption{ Definition of Essence using Old Syntax } \label{UglyEssence}
\end{figure}

@@

Isabelle/HOL's Sledgehammer tool, which orchestrates calls to
external provers such as \textsc{Leo-II}, still
fails to detect the inconsistency of G\"odel's axioms (in the standard
embedding), while a direct modeling of the problem in TPTP THF syntax
in combination with a direct call of \textsc{Leo-II} succeeded. In
other words, without independent experiments directly in TPTP THF the
inconsistency would thus not have been detected.
\begin{figure*}
\centerline{
\includegraphics[width=.65\textwidth]{./Images/Manuscript2.png} \hfill
\includegraphics[width=.35\textwidth]{./Images/Inconsistency_S5U_direct.png}
}
\caption{(a) G\"{o}del's manuscript, with mutually inconsistent axioms and
  definitions highlighted; (b) Refutation in
\SFiveU} \label{Inconsistency_S5U} \label{GoedelScript} 
\end{figure*}

>>>>

\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

% \begin{figure*}
%   \centering
%   \begin{subfigure}[t]{0.4\textwidth}
%     \includegraphics[width=\textwidth]{./Images/Scott_S5U.png}
%     \caption{Full Automation of T3 in \SFiveU; Consistency of Scott's
%       Axioms;  Automatic Verification of Modal Collapse} \label{Scott_S5U}
%   \end{subfigure}
%   ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
%   % (or a blank line to force the subfigure onto a new line)
%   \begin{subfigure}[t]{0.4\textwidth}
%     \includegraphics[width=\textwidth]{./Images/QML_S5U.png}
%     \caption{Improved Embedding of \SFiveU} \label{QML_S5U}
%   \end{subfigure}
%   ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
%   % (or a blank line to force the subfigure onto a new line)
%   \begin{subfigure}[t]{0.4\textwidth}
%     \includegraphics[width=\textwidth]{./Images/Inconsistency_S5U_direct.png}
%     \caption{Inconsistency  in \SFiveU} \label{Inconsistency_S5U} 
%   \end{subfigure}
%   \begin{subfigure}[t]{0.4\textwidth}
%     \centerline{\includegraphics[width=\textwidth]{./Images/InconsistencyIsabelleK.png}}
%     \caption{Refutation of G\"odel's Axioms in Isabelle/HOL.} \label{InconsistencyIsabelleK}
%   \end{subfigure}
% \end{figure*}

@@

\begin{figure}
\centerline{\includegraphics[width=.95\columnwidth]{./Images/UglyEssence.png}}
\caption{Definition of Essence using Old Syntax} \label{UglyEssence}
\end{figure}

@@

Isabelle/HOL's Sledgehammer tool, which orchestrates calls to
external provers such as \textsc{Leo-II}, still
fails to detect the inconsistency of G\"odel's axioms (in the standard
embedding), while a direct modeling of the problem in TPTP THF syntax
in combination with a direct call of \textsc{Leo-II} succeeded. In
other words, without independent experiments directly in TPTP THF the
inconsistency would thus not have been detected.
\begin{figure*}
  \centering
  \begin{subfigure}[t]{0.72\textwidth}
    \includegraphics[width=\textwidth]{./Images/Manuscript2.png}
    \caption{G\"{o}del's manuscript, with mutually inconsistent axioms and
      definitions highlighted} \label{GoedelScript} 
  \end{subfigure}
   \begin{subfigure}[t]{0.27\textwidth}
     \includegraphics[width=\textwidth]{./Images/Inconsistency_S5U_direct.png}
     \caption{ Inconsistency in \SFiveU} \label{Inconsistency_S5U} 
   \end{subfigure}
% \includegraphics[width=.73\textwidth]{./Images/Manuscript2.png} \hfill
% \includegraphics[width=.26\textwidth]{./Images/Inconsistency_S5U_direct.png}
% \caption{(a) G\"{o}del's manuscript, with mutually inconsistent axioms and
%   definitions highlighted; (b) Inconsistency in \SFiveU} \label{GoedelScript} \label{Inconsistency_S5U} 
\end{figure*}
